\addchapter{参考文献}
\begin{thebibliography}{99}% 文献数が10未満の時 {9}，10～99の時 {99}
%\addchapter{参考文献}
\bibitem{rec_text}
Dietmar Jannach,Markus Zanker, Alexander Felfernig,Gerhard Friendrich,
(田中克己,角谷和俊).
情報推薦システム入門,pp.13-21,共立出版,2012.
\bibitem{user-based-collaborative-filtering}
Resnick, Paul and Iacovou, Neophytos and Suchak, Mitesh and Bergstrom, Peter and Riedl, John.
GroupLens: an open architecture for collaborative filtering of netnews,
Proceedings of the 1994 ACM conference on Computer supported cooperative work,pp.175-184,1994.
\bibitem{item-based-collaborative-filtering}
Badrul Sarwar, George Karypis, Joseph Konstan, John Riedl.
Item-based collaborative filtering recommendation algorithms,
Proceedings of the 10th international conference on World Wide Web, pp.285-295, ACM Press, 2001.

\bibitem{content-based-filtering}
P. Lops, M. de Gemmis, and G. Semeraro.
Content-based recommender systems: State of the art and trends,
In Recommender Systems Handbook, pages 73-105. 2011.


\bibitem{svm}
C. Cortes and V. Vapnik. "Support vector networks". Machine Learning, 20:pp.273-297, 1995.

\bibitem{neural-network}
J. Hertz, A. Krogh and R. G. Palmer. Introduction to the theory of neural computation, Vol. 1, Basic Books, 1991.

\bibitem{copulaInf}
Carsten Eickhoff, Arjen P de Vries, and Kevyn Collins Thompson.
Copulas for information retrieval.
In Proceedings of the 36th international ACM SIGIR conference
on Research and development in information retrieval, pp. 663--672. ACM, 2013.

\bibitem{copulaEickhoff}
Carsten Eickhoff and Arjen P de Vries.
Modelling complex relevance spaces with copulas.
In Proceedings of the 23rd ACM International Conference on Conference on Information and Knowledge Management,
pages 1831–-1834. ACM, 2014.

\bibitem{Komatsuda}
Takuya Komatsuda, Atsushi Keyaki, and Jun Miyazaki.
A Score Fusion Method Using a Mixture Copula,
27th International Conference on Database and Expert Systems Applications (DEXA 2016),
Volume 9828 of LNCS, pp.216-232, Porto,
September 2016.

\bibitem{Suzuki}
鈴木崇弘, 欅 惇志, 宮崎 純.
コピュラを用いたユーザープロファイリング手法の提案,
第9回データ工学と情報マネジメントに関するフォーラム（DEIM Forum 2017）論文集,A7-1.

\bibitem{Scott}
D.W.Scott,
"Multivariate Density Estimation:\\
Theory,Practice,and,Visualization",
John Wiley\&Sons,
New York,
Chicester,
1992.

\bibitem{Silverman}
B.W.Silverman,
"Denstyity Estimation for Statistics and Data Analysis.",
Vol.26,
Monographs on Statistics and Applied Probability,
Chapman and Hall,
London,
1986.

\bibitem{kl-divergence}
S. Kullback and R. A. Leibler.
On information and sufficiency,
The Annals ofMathematical Statistics, 22:pp.79-86, 1951.

\bibitem{sklar}
Sklar, A.
Functions de Repartition an Dimension Set Leursmarges,
Publications de L’In-stitut de Statistique de L’Universite de Paris, 1959.

\bibitem{k-means}
J. A. Hartigan and M. A. Wong.
Algorithm AS 136: A k-means clustering algorithm,
Applied statistics, pp. 100-108, 1979.

\bibitem{recOku}
奥健太, 中島伸介, 宮崎純, 植村俊亮, 加藤博一.
情報推薦におけるユーザーの価値判断基準モデルに
基づくコンテキスト依存型ランキング方式,
情報処理学会論文誌, データベース, Vol.2,
No.1(TOD 41), pp.57-80（2009）.

\bibitem{robust-stat}
Huber, P. J. (1981). Robust statistics. New York: John Wiley.

\bibitem{rankingSVM}
  Herbrich, Ralf and Graepel, Thore and Obermayer, Klaus.
  Support vector learning for ordinal regression,
  Proceedings of the 9th international conference on Artificial Neural Networks,
  IET, pp.97-102, 1999,

\bibitem{rankingSVMTool}
T. Joachims.
Training Linear SVMs in Linear Time,
Proceedings of the ACM Conference on Knowledge Discovery and Data Mining (KDD), 2006.

\bibitem{IR-1}
Ronan Cummins.
Measuring the ablity of score distributions to model relevance.
In \it{Information Retrieval Technology},
\rm
pp.25-36.
Springer,2011.

\bibitem{IR-2}
EdWard A Fox and Joseph A Shaw.
Combination of multiple searches.
\it{NIST SPECIAL PUBLICATION SP},
\rm
pp.243-243,1994.

\bibitem{IR-3}
Evangelos Kanoulas,Keshi Dai, Virgil Pavlu, and Javed A Aslam.
Score distribution models: assumptions, intuition, and robustnesss to score manipulation.
In \it{Proceedings of the 33rd international ACM SIGIR conference on Research and development in information retrieval},
\rm
pp.242-249.
ACM,
2010.

\end{thebibliography}
